03 Data Vizualization

### 2022-04-06 03_data_viz.Rmd
added save

```{r}
p_abundance_v_turnover <- turnover %>% 
  filter(inc_time_d != 0) %>% 
  ggplot(aes(
    x = compound_ug_per_g_soil,
    y = u_d,
    color = dF*10000
  )) +
  facet_wrap(vars(inc_time_d, soil), ncol = 3) +
  geom_point(alpha = 0.6) +
  scale_color_viridis_c() +
  theme_bw() +
  labs(x = "µg analyte per g soil",
       y = TeX("Turnover (d$^{-1}$)"),
       color = TeX("$ \\Delta ^2H$ (ppm)")
  ) +
  guides(color = guide_colorbar(barwidth = 0.5)) +
  theme(
    strip.background = element_blank(),
    panel.grid = element_blank(),
  )
p_abundance_v_turnover
```

>>>>

```{r}
p_abundance_v_turnover <- turnover %>% 
  filter(inc_time_d != 0) %>% 
  ggplot(aes(
    x = compound_ug_per_g_soil,
    y = u_d,
    color = dF*10000
  )) +
  facet_wrap(vars(inc_time_d, soil), ncol = 3) +
  geom_point(alpha = 0.6) +
  scale_color_viridis_c() +
  theme_bw() +
  labs(x = "µg analyte per g soil",
       y = TeX("Turnover (d$^{-1}$)"),
       color = TeX("$ \\Delta ^2H$ (ppm)")
  ) +
  guides(color = guide_colorbar(barwidth = 0.5)) +
  theme(
    strip.background = element_blank(),

    panel.grid = element_blank(),
  )
p_abundance_v_turnover

cowplot::save_plot(filename = "fig_output/abundance_v_turnover.pdf",
                   plot = p_abundance_v_turnover,
                   base_height = 6,
                   base_width = 8)
```
